Contextual Combinatorial Cascading Bandits

### 2015-12-04 contextual combinatorial cascading bandits.tex
reorganize main theorem

This theorem states that with high probability, the estimate $\hat{\theta}$ lies in the ellipsoid centered at $\theta_*$  with confidence radius $\beta_t(\delta)$ under $\bV_t$ norm. Building on this, we can define an upper confidence bound of the expected weight of base arm $a$ by
\begin{equation}
\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}.
\end{equation}

@@

\STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
\STATE {$\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$}
\STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
%\STATE {}

@@

Here is our main theorem.
\begin{theorem}
\label{thm:main}
Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_k' = 1 - \gamma_k, \gamma'_K \geq \frac{1}{4}f_{\wedge}^{\ast}$. Let regularization parameter satisfy $\lambda \geq C_\gamma$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, {\em ConComCascade} for both conjunctive and disjunctive objectives, satisfy
\begin{align}
&R(T) = O(\frac{d}{p^*} \log(C_\gamma T) \sqrt{KT}),\\
&R_{\wedge}(T) = O(\frac{d}{f_{\wedge}^{\ast}} \log(C_\gamma T) \sqrt{KT}).
\end{align}
where
\begin{align*}
&f^* = \min_{1 \leq t \leq T} f_t^{\ast},\\
&f_{\wedge}^* = \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},\\
&C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K-1} (1 - \gamma_k')^2 = O(K),
\end{align*}
and $p_{t, \bA_t}$ and $p_{\wedge, t, \bA_t}$ are probabilities that all base arms of $\bA_t$ have been observed
\begin{align*}
&p_{t, \bA_t} = \PP(\bO_t \geq \abs{\bA_t}) = \prod_{k=1}^{\abs{\bA_t}-1} (1 - \theta_{\ast}^{\top} x_{t, \ba_k^t}),\\
&p_{\wedge, t, \bA_t} = \PP(\bO_{\wedge, t} \geq \abs{\bA_t}) = \prod_{k=1}^{\abs{\bA_t}-1} (\theta_{\ast}^{\top} x_{t, \ba_k^t}),\\
&p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}.
\end{align*}
\end{theorem}

To prove theorem \ref{thm:main}, we could start from estimating $\EE[\Delta_{t, \bA_t}|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
\begin{lemma}
\label{lem:DeltaEstimate}
For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
$$
\Delta_{t,A} \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
$$
if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
$$
\Delta_{\wedge, t,A} \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}

@@

\begin{proof}[ of lemma \ref{lem:DeltaEstimate}]
By lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by lemma \ref{lem:increasing},
$$
f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
$$
By lemma \ref{lem:estimateTech} and the definition of $\bU_t$ (\ref{eq:defU}),
$$
f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
Because $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, then 
$$
f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
Therefore,
$$
\Delta_{t, A} = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
The result for the disjunctive case can be deduced similarly.
\end{proof}

\begin{lemma}
\label{lem:prefixRelation}
Suppose 
% $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and 
$0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. 
% For the conjunctive case, it holds that
% $$
% p_A \geq 1 - \frac{f(A, w)}{\gamma_{\abs{A}}}.
% $$
Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then for the problem with disjunctive objective and $k < \abs{A}$, we have the following properties:
\begin{itemize}
\item[(1)] $f_{\wedge}(A, w) \leq \gamma_{\abs{A}}' + (1 - \gamma_{\abs{A}}') p_{\wedge, A}$;
\item[(2)] $f_{\wedge}(B_{k+1}, w) \leq f_{\wedge}(B_k, w)$;
\item[(3)] $p_{\wedge, B_{k+1}} \leq p_{\wedge, B_k}$;
\item[(4)] $f_{\wedge}(B_k, w) \leq \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{B_{k+1}}$.
\end{itemize}
\end{lemma}

@@

\begin{lemma}
Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the disjunctive objective, there exists a prefix $B$ of $A$ such that 
$$
p_{\wedge, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad \Delta_{\wedge, t, B} \geq \frac{1}{2}\Delta_{\wedge, t, A}.
$$ 
\end{lemma}
\begin{proof}
If $f_{\wedge}(A, w) \geq \frac{1}{2} f_{\wedge, t}^{\ast}$, then by lemma \ref{lem:prefixRelation},
$$
p_{A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'.
$$

Suppose $f_{\wedge}(A, w) \leq \frac{1}{2} f_{\wedge, t}^{\ast}$. Let
$$
x_k = f_{\wedge}(B_k,w), ~~ y_k = \gamma_k' + (1 - \gamma_k')p_{\wedge, B_k}, ~~I_k = [x_k, y_k]
$$
Then by lemma \ref{lem:prefixRelation}, we have $x_k \leq y_k$, $x_{k+1} \leq x_k \leq y_{k+1}$. Therefore, $I_k$ is indeed an interval and $I_k \cap I_{k+1} \neq \emptyset$. Also, $x_{\abs{A}} = f_{\wedge}(A, w)$ and $y_1 = 1$. Thus
$$
[f_{\wedge}(A,w), 1] = \bigcup_{k=1}^{\abs{A}} I_k.
$$
Then there exists a $k$ such that $\frac{1}{2}f_{\wedge, t}^{\ast} \in I_k$:
$$
f_{\wedge}(B_k,w) \leq \frac{1}{2}f_{\wedge, t}^{\ast} \leq \gamma_k' + (1 - \gamma_k')p_{\wedge, B_k}
$$
Therefore, the results are derived.
\end{proof}

\begin{proposition}
Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for all time $t$. Then
$$
E[\Delta_{t, \bA_t}|\cH_t] \leq \frac{1}{p^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}
$$
If we have
% $$
% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
% $$
$$
\gamma_K' \geq \frac{1}{4} f_{\wedge}^{\ast},
$$
then
\begin{align*}
% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
&E[\Delta_{\wedge, t, \bA_t}|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},
\end{align*}
where $f^{\ast} = \max_{t} f_t^{\ast}, f_{\wedge}^{\ast} = \max_{t} f_{\wedge, t}^{\ast}$.
\end{proposition}
\begin{proof}
For the conjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.

For the disjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $\Delta_{\wedge, \bB_t} \geq \frac{1}{2}\Delta_{\wedge, A}$. Then we have
$$
\EE_t[\Delta_{\wedge, t, \bA_t}] \leq \frac{8}{f_{\wedge, t}^*} \EE_t[\Delta_{\wedge, t, \bB_t} \bOne\{\Delta_{\wedge, t, \bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
$$
Because 
$$
f_{\wedge}(A_t^*, \theta_*^{\top}X_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t)
$$
by lemma \ref{lem:increasing} and
$$
f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\beta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
by lemma \ref{lem:estimateTech}, we have
$$
\Delta_{\wedge, t, \bB_t} \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
\end{proof}

@@

\begin{proof}[ of theorem \ref{thm:main}]
Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$.

For the conjunctive case,
\begin{equation}
\begin{split}
&R(T) =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
&\leq \EE[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t[\beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]]\\
&\leq \EE[\sum_{t=1}^{T} \frac{1}{p^*} \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]} ]  \\
&\leq O(\frac{d}{p^*} \log(C_\gamma T)\sqrt{TK}).
\end{split}
\end{equation}

For the disjunctive case, 
\begin{equation}
\begin{split}
&R(T) =\sum_{t=1}^{T} \EE_{t}[\Delta_{\wedge, t, \bA_t}] \\
&\leq \EE[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}] \\
&\leq \EE[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
&\leq \EE[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE_t[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}]\\
&\leq O(\frac{d}{f_{\wedge}^{\ast}}\log(C_\gamma T)\sqrt{TK}).
\end{split}
\end{equation}
\end{proof}

>>>>

This theorem states that with high probability, the estimate $\hat{\theta}$ lies in the ellipsoid centered at $\theta_*$  with confidence radius $\beta_t(\delta)$ under $\bV_t$ norm. Building on this, we can define an upper confidence bound of the expected weight of base arm $a$ by
\begin{equation}
\label{eq:defU}
\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}.
\end{equation}

@@

\STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
\STATE {$\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$}
\STATE {//In the conjunctive case, use $f_{\wedge}$ in stead of $f$}
\STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
%\STATE {}

@@

To state our main theorem, we need some definitions. Let
$$
f_{\wedge}^* = \max_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
$$
denote the best expected reward in all time under the conjunctive objective and let $p_{t, \bA_t}$ (resp., $p_{\wedge, t, \bA_t}$) are probabilities that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ have been observed under disjunctive objective(resp., conjunctive), that is 
\begin{align*}
&p_{t, A} = \prod_{k=1}^{\abs{A}-1} (1 - \theta_{\ast}^{\top} x_{t, a_k^t}),\\
&p_{\wedge, t, A} = \prod_{k=1}^{\abs{A}-1} (\theta_{\ast}^{\top} x_{t, a_k^t}).
\end{align*}
We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed under disjunctive case. Here is our main theorem.
\begin{theorem}
\label{thm:main}
Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and 
$$
\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}.
$$
Let regularization parameter satisfy $\lambda \geq C_\gamma$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, {\em ConComCascade} for both conjunctive and disjunctive objectives, satisfy
\begin{equation}
\begin{split}
&R(T) = \frac{\sqrt{2}}{p^*} (\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda}) \\
&\qquad \qquad \cdot \sqrt{TKd\log(\lambda + C_\gamma T/d)},
\end{split}
\end{equation}
\begin{equation}
\begin{split}
&R_{\wedge}(T) = \frac{\sqrt{128}}{f_{\wedge}^{\ast}} (\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda})\\
&\qquad \qquad \cdot \sqrt{TKd\log(\lambda + C_\gamma T/d)}.
\end{split}
\end{equation}
where
\begin{align*}
C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K} (1 - \gamma_k')^2 \in [1, K].
\end{align*}
\end{theorem}

To prove Theorem \ref{thm:main}, we could start from estimating $\EE[\Delta_{t, \bA_t}|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
\begin{lemma}
\label{lem:DeltaEstimate}
For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
$$
\Delta_{t,A} \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
$$
if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
$$
\Delta_{\wedge, t,A} \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}

@@

\begin{proof}[ of Lemma \ref{lem:DeltaEstimate}]
By Lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by Lemma \ref{lem:increasing},
$$
f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
$$
By Lemma \ref{lem:estimateTech} and the definition of $\bU_t$ \eqref{eq:defU},
$$
f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
Because $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, then 
$$
f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
Therefore,
$$
\Delta_{t, A} = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
The result for the disjunctive case can be deduced similarly.
\end{proof}

\begin{lemma}
\label{lem:prefixRelation}
Suppose 
% $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and 
$0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. 
% For the conjunctive case, it holds that
% $$
% p_A \geq 1 - \frac{f(A, w)}{\gamma_{\abs{A}}}.
% $$
Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then for the problem with conjunctive objective and $k < \abs{A}$, we have the following properties:
\begin{itemize}
\item[(1)] $f_{\wedge}(A, w) \leq \gamma_{\abs{A}}' + (1 - \gamma_{\abs{A}}') p_{\wedge, A}$;
\item[(2)] $f_{\wedge}(B_{k+1}, w) \leq f_{\wedge}(B_k, w)$;
\item[(3)] $p_{\wedge, B_{k+1}} \leq p_{\wedge, B_k}$;
\item[(4)] $f_{\wedge}(B_k, w) \leq \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{B_{k+1}}$.
\end{itemize}
\end{lemma}

@@

\begin{lemma}
Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
$$
p_{\wedge, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad \Delta_{\wedge, t, B} \geq \frac{1}{2}\Delta_{\wedge, t, A}.
$$ 
\end{lemma}
\begin{proof}
If $f_{\wedge}(A, w) \geq \frac{1}{2} f_{\wedge, t}^{\ast}$, then by Lemma \ref{lem:prefixRelation},
$$
p_{\wedge, A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'.
$$

Suppose $f_{\wedge}(A, w) \leq \frac{1}{2} f_{\wedge, t}^{\ast}$. Let
$$
x_k = f_{\wedge}(B_k,w), ~~ y_k = \gamma_k' + (1 - \gamma_k')p_{\wedge, B_k}, ~~I_k = [x_k, y_k]
$$
Then by Lemma \ref{lem:prefixRelation}, we have $x_k \leq y_k$, $x_{k+1} \leq x_k \leq y_{k+1}$. Therefore, $I_k$ is indeed an interval and $I_k \cap I_{k+1} \neq \emptyset$. Also, $x_{\abs{A}} = f_{\wedge}(A, w)$ and $y_1 = 1$. Thus
$$
[f_{\wedge}(A,w), 1] = \bigcup_{k=1}^{\abs{A}} I_k.
$$
Then there exists a $k$ such that $\frac{1}{2}f_{\wedge, t}^{\ast} \in I_k$:
$$
f_{\wedge}(B_k,w) \leq \frac{1}{2}f_{\wedge, t}^{\ast} \leq \gamma_k' + (1 - \gamma_k')p_{\wedge, B_k}
$$
Therefore, the results are derived.
\end{proof}

\begin{proposition}
Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for all time $t$. Then
$$
E[\Delta_{t, \bA_t}|\cH_t] \leq \frac{1}{p^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}
$$
If we have
% $$
% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
% $$
$$
\gamma_K' \geq \frac{1}{4} f_{\wedge}^{\ast},
$$
then
\begin{align*}
% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
&E[\Delta_{\wedge, t, \bA_t}|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},
\end{align*}
where $f^{\ast} = \max_{t} f_t^{\ast}, f_{\wedge}^{\ast} = \max_{t} f_{\wedge, t}^{\ast}$.
\end{proposition}
\begin{proof}
For the disjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.

For the conjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $\Delta_{\wedge, \bB_t} \geq \frac{1}{2}\Delta_{\wedge, A}$. Then we have
$$
\EE_t[\Delta_{\wedge, t, \bA_t}] \leq \frac{8}{f_{\wedge, t}^*} \EE_t[\Delta_{\wedge, t, \bB_t} \bOne\{\Delta_{\wedge, t, \bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
$$
Because 
$$
f_{\wedge}(A_t^*, \theta_*^{\top}X_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t)
$$
by Lemma \ref{lem:increasing} and
$$
f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\beta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
by Lemma \ref{lem:estimateTech}, we have
$$
\Delta_{\wedge, t, \bB_t} \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
\end{proof}

@@

\begin{proof}[ of Theorem \ref{thm:main}]
Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$.

For the conjunctive case,
\begin{equation}
\begin{split}
&R(T) =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
&\leq \EE[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t[\beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]]\\
&\leq \EE[\frac{1}{p^*} \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]} ]  \\
&\leq \EE[\frac{1}{p^*} (\sqrt{\log(\det(\bV_t)) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda}) \\
&\qquad \qquad \cdot \sqrt{TK \cdot 2\log(\det(\bV_t))} ]\\
&\leq \frac{\sqrt{2}}{p^*} (\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda})\\
&\qquad \qquad \cdot \sqrt{TKd\log(\lambda + C_\gamma T/d)} ]
\end{split}
\end{equation}

For the disjunctive case, 
\begin{equation}
\begin{split}
&R(T) =\sum_{t=1}^{T} \EE_{t}[\Delta_{\wedge, t, \bA_t}] \\
&\leq \EE[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}] \\
&\leq \EE[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
&\leq \EE[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE_t[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}]\\
&\leq \EE[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} (\sqrt{\log(\det(\bV_t)) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda}) \\
&\qquad \qquad \cdot \sqrt{TK \cdot 2\log(\det(\bV_t))} ]\\
&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} (\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda})\\
&\qquad \qquad \cdot \sqrt{TKd\log(\lambda + C_\gamma T/d)} ]
\end{split}
\end{equation}
\end{proof}
